\chapter*{Acknowledgments}
\addcontentsline{toc}{chapter}{Acknowledgements}
\markboth{Acknowledgements}{Acknowledgements}
\vspace{-5mm}

% When I was young I always wanted to pursue a scientific career. The pursuit of achieving my doctorate's degree has been by far the largest and heaviest stepping stone in that career. I have been extremely fortune not only in the opportunities that (sometimes seemingly) I've been given but also with the relations that have fruited over the past years.

% It is no secret that without these individuals I'd be unable to reach these achievements in life.

As I embark on the end of my PhD journey, I am somewhat reminded of the Latin motto of the Eindhoven University: ``\textit{Mens agitat molem},'' which translates to ``\textit{Mind moves the mass}.'' This beautiful phrase perhaps encapsulates the essence of my academic pursuit, where other minds played a pivotal role in influencing and reshaping the world around me. Throughout my PhD, I have had the extreme privilege of connecting with various brilliant scholars, mentors, fellow students, and (new) friends who have expanded my understanding within the areas of research, but more importantly, beyond such scopes. ``textit{Mens agitat molem}'' is evident in the collaborative discussions, debates, exchanges of ideas, and connections that have fueled my personal growth and pushed me -- the metaphorical ``mass'' -- forward throughout these years.

First, I would like to express my gratitude to my first promotor. Henk, ik wil je bedanken  voor alle mogelijkheden die je mij hebt geboden tijdens en vooraf mijn promotietraject. Ik heb het gevoel dat onze visie voor het veld 'soft robotics' altijd parallel heeft gelopen, en dit heeft niet alleen geleid tot een uiterst prettige samenwerking, maar heeft mij ook de vrijheid gegeven om mijzelf als onderzoeker vrij te ontwikkelen. Je scherpe opmerkingen, maar vooral ook je humoristische inbreng, werden zeer gewaardeerd. Je begeleiding, steun, en expertise hebben mij geholpen om mijn promotietraject tot een succesvol einde te brengen. Bedankt voor alles.

Secondly, I would like to express my sincere appreciation to my co-promoter, Sasha. I am immensely grateful for your unwavering support and open-mindedness throughout the years, but above all, for your remarkable patience with me. You have consistently provided me with the freedom to explore new ideas, and we have engaged in numerous captivating discussions connected to the realm of soft robotics. Furthermore, I deeply value the time and availability you have dedicated to me, even without prior notice. This has truly made me feel that your doors are always open – a practice that I have come to embrace with my own students over the course of my Ph.D. career.

My sincere gratitude also goes to the committee members who have been part of reviewing the thesis and participating in the public defense: Jaap den Toonder, Gijs Krijnen, Bas Overvelde, and Anibal Ollero; and my gratitude to Patrick Anderson who agreed to chair the defense ceremony.

I would also like to express my gratitude to the members of the {Wearable Robotics} project. Herman, thank you for assembling such a wonderful and diverse group of researchers. The monthly telecoms and yearly consortia that brought us together were inspirational and insightful, and I thoroughly enjoyed the platform that was given for discussions and collaboration. Ali, thank you for all the fruitful collaboration, and I am proud of our collaboration and publication, which has become a chapter of your dissertation. What an honor to be part of your doctoral work! Mariska, thank you for all your interesting input and the opportunities you have given Ali and me to gain insight into the clinical world. I also want to thank the other fantastic researchers from Twente: Martijn, Cristina, Alejandro, Ander, Michelle, and the folks from Delft, Cor, and Wouter; you guys are truly inspiring engineers.

I am deeply grateful to my wonderful ex-colleagues with whom I have had the pleasure of working on various courses: Astrid, Bayu, Carlos, Ines, Nathan, Matt, and Ruben, and a few others I'd like to mention separately. Alessandro, I want to express my heartfelt appreciation for our collaboration on the robotics course. Your consistent interest in my project and the occasional interesting emails on related research topics have been truly valuable. Irene, bedankt voor onze vlekkeloze samenwerking tijdens de Haptics en voor het verwelkomen in jullie onderzoeksgroep en lab. Rob, ik heb oprecht genoten van onze samenwerking bij Dynamics, maar wat ik het meest bewonder, is jouw standvastige aanwezigheid tijdens de ``Vrijmibo'', zowel in persoon als virtueel. Gerard, bedankt voor de boeiende discussies die we hebben gehad onder het genot van een kopje koffie. Ik wil ook graag Harry, Peter (2x) erkennen voor hun lab ondersteuning. Tot slot, Geertje, hartelijk dank voor alles wat je hebt gedaan. De zorg die je hebt voor onze groep, maar ook voor elk individu, blijft niet onopgemerkt. Jij bent werkelijk de steunpilaar van onze groep. Thank you all for making my time at the TU/e memorable and rewarding.

To the students I had the pleasure of supervising: Erwin, Sef, Willem, Has, and Yoshi, and a few others I'd like to mention separately. Benn, I feel extremely lucky that, out of all the students who rejected my B.Sc project proposal, you were the one to give it a shot. Call it fate. I was thrilled to hear you had joined our group, and I now know the ``Vrijmibo'' is in good hands. Hoang, it was a pleasure supervising you. Thanks for the ergonomic mouse which I am still using while finishing up these last pages. Also, Tijn, thanks for the extremely nice collaboration. It was a pleasure reading all of your ``extensive'' reports, and I was surprised by your kind words in the acknowledgements of your thesis.

I would also like to express my heartfelt gratitude to my former office mates. Tom, ik ben dankbaar voor de begeleiding en steun die je hebt geboden tijdens de begindagen als jonge promovendus. Ook onze samenwerkingen op jouw CAD-gerelateerde projecten voor de fiets waren echt vermakelijk. Rinus, bedankt voor jouw luisterend oor en betrokkenheid bij allerlei interessante discussies op kantoor. Ik zal onze uitgebreide whiteboard discussies missen, die immers essentieel zijn geweest voor de vormgeving van deze scriptie. Jouw aanwezigheid als kantoorgenoot is waardevol geweest, vooral wanneer ik een extra `\emph{mind}' nodig had om mentale blokkades te verhelpen. Ana, I will cherish the memories of our delightful coffee breaks and the engaging discussions we had, particularly the ones we shared digitally from my kitchens during the pandemic. I am also grateful for the opportunity to publish together. Lastly, I would like to acknowledge Guo and Nishant, albeit our time together in the office was brief, your contributions and camaraderie were greatly appreciated. 

Also thanks to all my fellow Ph.D.s who've I had to pleasure to share the occasional coffee. Thanks to my other coworkers from D\&C: Alexander, Andy, Bas, Dirk, Dipankar, Fahim, Haleh, Jizheng, Joey, Kaidong, Kevin, Lars (2x), Luuk (2x), Maarten, Philipp, Rapha\"{e}l, Raul, Roeland, Rigo, Sebastiaan, Semih, Viral, Wouter (2x), and Yuzhe; and the folks from CST: Bardia, Casper, Hao, Jilles, Koen (2x), Leontine, Maurice, Max, Nard, Noud, Paul, Puck, Roy, Sven, and Tomas. Also thanks to all the older former colleagues that have improved the Ph.D. experience significantly: Alex, Chyannie, Daniel (2x), Frans, Igor, Kirill, Lennart, Leroy, Michiel, Quentin, Robert, Rishi, Ruud, Sajad, Suraj, and Veronica.

There are a few colleagues I'd like to mention separately. Krishna, your unbreakable optimism and your laugh that echoes through the halls of Gemini-South are seriously infectious and uplifting. Thanks for all that you have organized. Dario and Alessia, thanks for all the nice Italian coffee and cookies -- grazie mille! Jari, hartelijk dank dat je me feitelijk gratis hebt meegenomen naar Rammstein. Het was een mooie gelegenheid waarop mijn ``lange-haar-fase'' zijn vruchten heeft afgeworpen. Ruud, hartelijk dank voor je sporadische bezoeken aan mijn kantoor, je aansporing om die ene keer naar de sportschool te gaan en al onze interessante filosofische discussies. Ricky, het was altijd een genoegen wanneer je langs kwam op kantoor. Mischa, it was a pleasure being my partner-in-crime when infiltrating the Benelux meeting. It was a legendary evening, by far the best Benelux meeting for me! Naturally, I have to extend my gratitude to Venkata for not showing up, so I could borrow his name tag, and all the other PhDs who heroically gifted all their beers to me. Femke and Mahboubeh, thank you for the fruitful collaborations. I was thrilled to see more people starting to work on soft robotics within our group, and I am delighted that we had the opportunity to publish together. A small shoutout to the people at AMOLF: Alberto, Mannus, Paul, Sergio, and (the legendary) Shibo; for a memorable experience at last year's Dutch Soft Robotics Symposium in Twente.
The same naturally applies to the folks of the Reshape group. Also special thanks to those that celebrated my hand-in date, those that pleasantly surprised me on my 30\textsuperscript{th} birthday, and the regulars at the ``\textit{VrijMiBo}''. To all of you, my heartfelt thanks for transforming my time at the University into an unforgettable, rewarding experience full of cherished friendships.

Camiel, ook bedankt voor al die vroege ochtendtreinritten. De mogelijkheid om alles aan jou voor te leggen hebben mij veel mentale rust gegeven en hebben deelsgeleid tot het succesvol afronden van dit boekje. Falco, bedankt voor je constante interesse, suggesties voor zelfverbeteringsboeken, game- en pizzanachten. Roos, bedankt voor je steun en levensadvies. Jullie zijn geweldige vrienden geweest gedurende al die jaren, een echte vangst! Martijn en Bob, bedankt voor alle whiskey-(maar voornamelijk speciaal bier)-avonden. Dank aan Anne en Britt voor alle ``gamy-gamy'' avonden, filmavonden, tripjes Groningen, en natuurlijk onze magische reis naar Londen -- kan niet wachten op een vervolg (of trilogie). Jullie vriendschap is essentieel motivatievoer geweest voor dit boekje. Gijs en Bob, bedankt voor het accepteren van de rol van paranymph, met twee van mijn oudste vrienden aan mijn zijde heeft de tegenpartij geen kans. Mijn dankbaarheid strekt zich natuurlijk ook uit naar de andere oldies Roel, Michel, en ook Panda. Xavier, bedankt voor al je frequente herinneringen om af te spreken. Dank aan Dominique voor het organiseren van al deze geweldige reizen en avonturen die we de afgelopen plus-tien jaar hebben gehad, grotendeels dankzij jouw fantastische organisatietalent. De recente Ardennen en Londen trip waren de hoognodige pauzes waar ik zo naar verlangde tijdens mijn promotieonderzoek. Ties, bedankt dat je altijd mijn vaste aanspreekpunt bent geweest voor alles wat met concerten te maken heeft. En vanzelfsprekend gaat mijn dank ook uit naar de andere old-timers: Cynthia, Siem, Jeffrey, Etienne, Jolijn en Dennis. Diem en Lissane, bedankt voor alle gezelligheid en de geweldige Foals LP die jullie hebben geschonken - mijn favoriet tot heden.

Manu und Nina, vielen Dank f\"{u}r eure Gastfreundschaft in R\"{o}dern, die Biere und das fantastische deutsche Essen, die speziellen, thematischen Geburtstagspartys - nat\"{u}rlich war Big Lewboski meine Lieblingsparty - und die Brettspielabende. Johannes, vielen Dank f\"{u}r dein wissenschaftliches Interesse, und Sarah, danke f\"{u}r deinen herzlichen Empfang in die Familie. Regina und Karsten, danke, dass ihr mich so in eure Familie einbezogen habt, so dass ich mich dazugeh\"{o}rig gef\"{u}hlt habe.

Mam, ik wil je enorm bedanken voor al je ongelofelijke support in zowel mijn persoonlijke ontwikkeling als mijn carrière. Jouw constante aanmoediging en steun vanaf het begin hebben eindelijk hun vruchten afgeworpen. Ik ben enorm dankbaar en trots dat ik jou als mijn moeder heb. Ook wil ik graag mijn broer, Myron of Madji, bedanken. De steun die jullie hebben aangeboden is ongelofelijk waardevol en heeft geleid tot het stand komen van deze thesis. Zonder jullie zou ik dit nooit hebben kunnen bereiken. Pap, bedankt voor je interesse en steun gedurende de afgelopen jaren. Jouw betrokkenheid heeft me altijd gemotiveerd en ge\"{i}nspireerd om het beste uit mezelf te halen. Ook Rachel verdient een speciale dankjewel, je betrokkenheid in onze familie is goud waard.

Also, thanks to those few I might have forgotten to mention. I have an exceptionally bad memory for names, but I won't easily forget a face.

Last but not least, my dearest Miriam, words cannot express the joy I have felt having you by my side during these ``\textit{tough}'' albeit ``\textit{adventurous}'' times. You were the light that has guided my soul to a safe and happy haven, and without you, I was probably not able to make it.

\begin{flushright}
Brandon Caasenbrood \\
Eindhoven, September 2023
\end{flushright}  