%!TEX root = ../../thesis.tex
\section{Concluding remarks}
\noindent In this chapter, we aimed to reduce the gap between modeling and control-oriented research in soft robotics. First, the dynamic models that describe the continuum-bodied motions need to be sufficiently accurate, and second the model must retain real-time performance to be applicable in control. By building upon the existing PCC models, we express the continuum deformation using a minimal set of coordinates related to the differential geometry of spatial curves; and explored FEM-based data to model the hyper-elasticity. To retain numerical efficiency, a reduced-order integration scheme is developed that efficiently computes the entries of the Lagrangian model through a Matrix-Differential equation; resulting in a continuum dynamical model for soft manipulators with real-time capabilities at minimal lost in numerical precision. 

The dynamic model has been extensively \editl analyzed \editr through simulations and experimental results. Not only does the dynamic models allow for real-time simulations with systems with various degrees of motion, it show good correspondence with the true physical soft robot. Furthermore, a passivity-based adaptive controller is proposed that provides good tracking performance even in the face of parameter uncertainties. The adaptive controller enables online estimation of the hyper-elastic stiffness and external loads, which further enhances the robustness toward modeling uncertainty undoubtedly present in soft robotics. In future work, we wish to further explore FEM-driven data for the parametrization of the spatial shape functions -- extending beyond constant-curvature, and employ the proposed controller methods to multi-link soft robots.
