%!TEX root = ../thesis.tex
%*********************************************************************************%
\chapter*{List of publications}
\addcontentsline{toc}{chapter}{List of publications}
\markboth{List of publications}{List of publications}
\newcommand{\ipj}{(\textit{in preparation for journal submission})}
\newcommand{\cur}{(\textit{under review})}
\newcommand{\sbm}{(\textit{submitted})}
\newcommand{\acp}{(\textit{accepted})}
\newcommand{\inp}{(\textit{in press})}

% \section*{Preliminary titles}
% \begin{enumerate}[leftmargin=2.5mm]
% \item A Control-oriented Perspective on Design and Modeling of Soft Robotic Systems;
% \item Towards a Unified Framework for Design and Model-based Control of Soft Robots;
% \item Addressing the Open Challenges in Soft Robotics: from Design to Model-based Control
% \item Design and Control Strategies for Soft Robotic Systems;
% \item Design, Modeling, Simulation and Control of Soft Robots.
% \item Design, Modeling and Control Strategies for Soft Robotics Systems;
% \item (Soft Manipulators/Soft Robotic Manipulators?)
% \end{enumerate}
%
% \section*{Preliminary committee members}
% \begin{itemize}[leftmargin=4mm]
% \item prof. J. den Toonder (TU/e, Microsystems, ICMS) \vspace{-2mm}
% \item dr. R. Luttge (TU/e, Microsystems) - Backup for Jaap \\ ............................................................................................... \vspace{-2mm}
% \item prof. G. Krijnen (Twente University) Technologies) \vspace{-2mm}
% \item prof. C.C.L. Wang (Delft University) \vspace{-2mm} \href{https://ieeexplore.ieee.org/document/9426391}{[1]}, \href{https://www.researchgate.net/publication/347965436_Jacobian-based_learning_for_inverse_kinematics_of_soft_robots}{[2]}
% \item prof R. Carloni (Rijksuniversiteit
% Groningen) - backup for Gijs \\ ............................................................................................... \vspace{-2mm}
% \item dr. E. Franco (Enrico, Imperial College London) \vspace{-2mm} \href{https://link.springer.com/article/10.1007/s11071-021-06817-1}{[1]}, \href{https://ieeexplore.ieee.org/document/9638969}{[2]}
% \item prof. H. Mochiyama (University of Tsukuba) \href{https://www.sciencedirect.com/science/article/pii/S2405896320328226?via%3Dihub}{[1]}, \href{https://ieeexplore.ieee.org/document/1242160}{[2]} \vspace{-2mm}
% \item dr. C. Duriez (INRIA Lille) \href{https://hal.inria.fr/hal-01370347/document}{[1]},\href{https://hal.archives-ouvertes.fr/hal-03192168/document}{[2]}\vspace{-2mm}
% \item prof. R. Katzschmann (ETH Zurich) \href{https://www.liebertpub.com/doi/pdfplus/10.1089/soro.2014.0022}{[1]},\href{https://arpi.unipi.it/retrieve/handle/11568/996018/683882/Final%20manuscript%20IEEE.pdf}{[2]}\vspace{-2mm}
% \item dr. S. Grazioso (University of Naples) \href{https://pubmed.ncbi.nlm.nih.gov/30481112/}{[1]} \vspace{-2mm}
% \item dr. M. Bächer (ETH Zurich) \href{https://pubmed.ncbi.nlm.nih.gov/31891526/}{[1]},\href{https://ieeexplore.ieee.org/document/9312179}{[2]}
% \item Antonio Bicchi - Italian
% \item Annibal Olero - Spain
% \item Bas Overvelde??
% \end{itemize}
\vspace{-10mm}
%*********************************************************************************%
\section*{Peer-reviewed journal articles}
\begin{itemize}[leftmargin=2mm]
  \item B. Caasenbrood, A. Pogromsky and H. Nijmeijer, “\textit{Generative Design of Soft Robotic Actuators -- a Gradient-based Approach}”, Frontiers in Robotics and AI, 2022. \ipj;
% \item B. Caasenbrood, A. Pogromsky and H. Nijmeijer, “\textit{Reduced-order Cosserat Models for Soft Robotic
%  Systems using FEM-driven Shape Reconstruction}”, Robotics and Automation Letters, 2022. \ipj;
%\item B. Caasenbrood, A. Amoozandeh Nobaveh, M. Janssen, A. Pogromsky, J. Herder, and H. Nijmeijer “\textit{An Energy-efficient Gravity-balancing Wrist Exoskeleton by exploring Compliant Beams and Soft Robotic Actuation},” Wearable Technologies. \ipj;
% \item A. Amiri, B. Caasenbrood, D. Liu, N. van de Wouw, and I. Lopez Arteaga, "\textit{An Electric Circuit Model for the Nonlinear Dynamics of Electro-active Liquid Crystal Coatings}", Applied Physics Letters, 2022. \sbm;
\item  B. Caasenbrood, A. Pogromsky and H. Nijmeijer, “\textit{Energy-shaping Controllers for Soft Robot Manipulators through Port-Hamiltonian Cosserat Models}”, SN Computer Science Springer, 2022;
\item B. Caasenbrood, A. Pogromsky and H. Nijmeijer, "\textit{Control-oriented Models for Hyper-elastic Soft Robots through Differential Geometry of Curves}”, Soft Robotics, 2022.
\end{itemize}

%*********************************************************************************%
\section*{Peer-reviewed articles in conference proceedings}
\begin{itemize}[leftmargin=2mm]
\item Chu, H., Caasenbrood, B. J., Keyvanara, M., Kuling, I. A., and Nijmeijer, H. (2023). \textit{"Full-body Grasping Strategy for Planar Underactuated Soft Manipulators using Passivity-based Control"}. IEEE International Conference on Soft Robotics (RoboSoft). IEEE.
\item Proper, B. W. B., Caasenbrood, B. J., and Kuling, I. A. (2023). \textit{"Easy Cleaning of 3D SLA/DLP Printed Soft Fluidic Actuators with Complex Internal Geometry"}. 2023 IEEE International Conference on Soft Robotics (RoboSoft). IEEE.
\item Caasenbrood, B. J., van Beek, F. E., Chu, H. K., and Kuling, I. A. (2022). \textit{"A Desktop-sized Platform for Real-time Control Applications of Pneumatic Soft Robots"}. 2022 IEEE 5th International Conference on Soft Robotics (RoboSoft). IEEE. 
\item B. Caasenbrood, F.E. van Beek, H. Khanh Chu, and I.A. Kuling, “\textit{A Desktop-sized Platform for Real-time Control Applications of Pneumatic Soft Robots},” IEEE International Conference on Soft Robotics, RoboSoft 2022, pp 217-223.
\item A. Amoozandeh Nobaveh, and B. Caasenbrood, "\textit{Design Feasibility of an Energy-efficient Wrist Exoskeleton
using Compliant Beams and Soft Actuators}", Proceedings of the 18th International  Consortium for Rehabilitation Robotics, 2022.
\item B. Caasenbrood, A. Pogromsky and H. Nijmeijer, "\textit{Energy-based control for Soft Robots using Cosserat-beam models}”, Proceedings of the 18th International Conference on Informatics in Control, Automation and Robotics, 2021, pp. 311–319.
\item B. Caasenbrood, A. Pogromsky and H. Nijmeijer, "\textit{A Computational Design Framework for Pressure-driven Soft Robots through Nonlinear Topology Optimization}," 2020 3rd IEEE International Conference on Soft Robotics, 2020, pp. 633-638.
\item B. Caasenbrood, A. Pogromsky and H. Nijmeijer, “\textit{Dynamic modeling of hyper-elastic soft robots using spatial curves},” IFAC World Congress, IFAC-Papers OnLine, 2020, pp. 9238-9243.
\end{itemize}

\section*{Talks, workshops, and non peer-reviewed abstracts}
\begin{itemize}[leftmargin=2mm]
\item Caasenbrood, B.J., invited student talk on  “\textit{Design and Control tools for fluidic soft robots},” 4TU Federation`s Symposium on Soft Robotics, Twente University, 2023.
\item Caasenbrood, B.J., invited talk on “\textit{3D-printed Soft Robotics},” Symposium on Robotic Technologies, Ultimaker, 2022. (invited speaker).
\item B. Caasenbrood, invited student speaker on \texttt{SOROTOKI}: \textit{an open-source MATLAB toolkit for Design, Modeling and Control of Soft Robots},”  4TU Federation`s Symposium on Soft Robotics, Delft University, 2022.
\item B. Caasenbrood, “\texttt{SOROTOKI}\textit{: an Open-source Toolkit for Soft Robotics written in MATLAB},”  IEEE International Conference on Soft Robotics, RoboSoft 2022, Edinbrugh. (poster presentation). Received the Best Poster Award during the workshop on "\textit{Software for Soft Robotics Research}". 
\item B. Caasenbrood, C. Della Santina, and A. Pogromsky, “\textit{Workshop on Model-based Control of Soft Robots},” European Control Conference (ECC), 2021. (main workshop organizer).
\item B. Caasenbrood, talk on  “\textit{Towards Design and Control of Soft Robotics},” 4TU Symposium on Soft Robotics (digital), 2020. (invited speaker).
\item B. Caasenbrood, talk on  “\textit{3D-printed Soft Robotics},” Symposium on Robotic Technologies, 2019. (invited speaker).
\item B. Caasenbrood, A. Pogromsky and H. Nijmeijer, talk on  “\textit{Forward Dynamics of Hyper-elastic Soft Robotics},” 39th Benelux Meeting on Systems and Control, 2019. (abstract).
\item B. Caasenbrood, A. Pogromsky and H. Nijmeijer, talk on  “\textit{Dynamical modeling and control of continuum soft robots},” 37th Benelux Meeting on Systems and Control, 2018. (abstract).
\end{itemize}
