%!TEX root = ../thesis.tex
\graphicspath{{2_Chapter/}}
\chapter{Modeling of Continuum Soft Robots -- Piece-wise Constant case}
{\let\thefootnote\relax\footnote{{\color{black}This chapter is based on: \\
\textit{1.} Caasenbrood, B. J., Pogromsky, A. Y., and Nijmeijer, H. (2020). \textbf{Dynamic modeling of hyper-elastic soft robots using spatial curves.} IFAC-PapersOnLine, 53, 9238–9243.\\[0.25em] \textit{2.} Caasenbrood, B. J., Pogromsky, A. Y., and Nijmeijer, H. (2021). \textbf{Dynamic Modeling of Hyper-elastic Soft Robots through Differential Geometry of Curves} Soft Robotics, 2021. (under review).
}}}
\label{chap:2}
\chaptermark{Chapter title for header}

\begin{chapter-abstract}
The motion complexity and use of exotic materials in soft robotics call for accurate and computationally efficient models intended for control. To reduce the gap between material and control-oriented research,we build upon the existing Piecewise-Constant Curvature framework by incorporating hyper-elastic and visco-elastic material behavior. In this work, the continuum dynamics of the soft robot are derived through the differential geometry of spatial curves, which are then related to Finite-Element data to capture the intrinsic geometric and material nonlinearities. To enable fast simulations, a reduced-order integration scheme is introduced to compute the dynamic Lagrangian matrices efficiently, which in turn allows for real-time (multi-link) models with sufficient numerical precision. By exploring the passivity and using the parametrization of the hyper-elastic model, we propose a passivity-based adaptive controller that enhances robustness towards material uncertainty and unmodeled dynamics -- slowly improving their estimates online. As a study case, a fully 3D-printed soft robot manipulator is developed, which shows good correspondence with the dynamic model under various conditions, e.g., natural oscillations, forced inputs, and under tip-loads. The solidity of the approach is demonstrated through extensive simulations, numerical benchmarks, and experimental validations.
\end{chapter-abstract}

\clearpage
\Materialtrue % enable chapter thumbs if disabled on chapter title page
%
%\section{Introduction}\label{chaptertitle:sec:introduction}
\sectionmark{Introduction}
\input{2_Chapter/2_Design/text.tex}

\clearpage
\input{2_Chapter/3_Model/text.tex}

\clearpage
\input{2_Chapter/4_MultiLink/text.tex}

\clearpage
\input{2_Chapter/5_Solver/text.tex}
%\blindtext
%
%
%\clearpage
%
%\section{Section title}\label{chaptertitle:sec:sectiontitle}
%\sectionmark{Section title for header}
%
%\blindtext
