%*********************************************************************************%
\chapter*{Societal summary}
\addcontentsline{toc}{chapter}{Societal summary}
\markboth{Societal summary}{Societal summary}

%*********************************************************************************%
% FROM "Information for Doctoral candidates"
%*********************************************************************************%

%Writing a public summary is part of the completion of PhD-projects at TU/e since 2017. It serves to open up the results of PhD-research to larger audiences, among which journalists and the general audience.

%The doctoral candidate writes the public summary of
%maximum 600 words
%before submitting form 2. Guidelines, examples and a template for writing a public summary can be found at www.tue.nl/promoties. The candidate sends the summary to the science information officers of CEC, via the upload form on the Promotions website. They will contact the doctoral candidate in order to jointly do editing, if necessary, and make sure the text is comprehensible and accessible.

%The final version of the summary will be published on the TU/e website, in the overview of PhD defenses. CEC draws the attention of journalists to this overview, and targets journalists directly with summaries. The summary will also be available online via the library.

%It is helpful if the candidate also supplies a picture, via the upload form. This may be a picture of the candidate, or a crucial part or result of the research. The picture will be included in the online overview of PhD’s, in landscape orientation and in quite small size. Therefore the content of the picture should be recognizable even in small size.
%Writing a public summary is not a prerequisite for graduation, but the university appreciates it very much if you do write one. In the department of Mechanical Engineering however the public summary (a.k.a. societal summary) is obligatory.

%*********************************************************************************%
Soft robotics is an emerging field that focuses on the design, development, and implementation of robots made from soft, flexible materials. Unlike traditional rigid robots, soft robots are able to mimic the movements and behaviors of living organisms, making them well-suited for a wide range of applications in fields such as healthcare, manufacturing, and exploration.

One of the main benefits of soft robotics is their ability to interact with humans and delicate objects in a safe and gentle way. Soft robots can be designed to be compliant and adaptable, allowing them to work in close proximity to people without causing harm. They can also be used in healthcare applications, such as wearable devices and prosthetics, where their flexibility and ability to conform to the human body can provide greater comfort and functionality than traditional rigid devices. Another advantage of soft robotics is their ability to operate in unstructured and unpredictable environments, such as disaster zones or outer space. Soft robots can change shape and adapt to their surroundings, making them more versatile and capable of performing a wide range of tasks. For example, soft robots can be designed to crawl through small spaces, squeeze through tight openings, and manipulate objects with greater precision than rigid robots.

However, there are also challenges associated with the development and implementation of soft robotics. One major challenge is the complexity of designing and controlling soft robots, which often require sophisticated algorithms and advanced materials. Additionally, there is a need for more research into the long-term durability and reliability of soft robots, particularly in harsh or extreme environments.

Despite these challenges, the potential benefits of soft robotics are significant, and the field continues to grow and evolve. As more researchers and engineers develop new materials, technologies, and applications for soft robots, we can expect to see these versatile and adaptable machines play an increasingly important role in our lives and society.
%IN ENGLISH:
%\lipsum[5-7]